The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-04 paper.tex
update

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated microwave spectra (colored lines in left) averaged over $20^{\circ}<|b|<30^{\circ}$, $|l|<10^{\circ}$.\
      The data point represents the \textit{WMAP} data in the 23 GHz K band and\
      the shaded bow-tie area indicates the range\
      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.\
      Simulated gamma-ray spectra (colored lines in right column)\
      of the \textit{Fermi} bubbles calculated for a longitude range of\
      $|l|<10^{\circ}$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.\
      The rows from top to bottom show the microwave (left) and gamma-ray (right) spectra\
      with CRe spectra index $p=2.2, 2.4$ and $2.6$.\
      The CRe cutoff energy is $1.1\times10^{6}m_{\text{e}}c^{2}$ in all cases.
      %At larger $p$, the microwave spectrum was found to be steeper as $I_{\nu}\propto \nu^{-(p-1)/2}$.
  }
  \label{fig__gammaRay}
\end{figure*}

>>>>

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated microwave spectra (colored lines in left) averaged over $20^{\circ}<|b|<30^{\circ}$, $|l|<10^{\circ}$.\
      The data point represents the \textit{WMAP} data in the 23 GHz K band and\
      the shaded bow-tie area indicates the range\
      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.\
      Simulated gamma-ray spectra (colored lines in right column)\
      of the \textit{Fermi} bubbles calculated for a longitude range of\
      $|l|<10^{\circ}$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.\
      The rows from top to bottom show the microwave (left) and gamma-ray (right) spectra\
      with CRe spectra index $2.2, 2.4$ and $2.6$.\
      The CRe cutoff energy is $1.1\times10^{6}m_{\text{e}}c^{2}$ in all cases.
      %At larger $p$, the microwave spectrum was found to be steeper as $I_{\nu}\propto \nu^{-(p-1)/2}$.
  }
  \label{fig__gammaRay}
\end{figure*}
